Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-09-20 manuscript/paper-tycho.tex
Run code with tweaked FWHMs, more paper writing

%\begin{CJK*}{UTF8}{gbsn}
\author{
Robert Petre\altaffilmark{1},
Sean M. Ressler\altaffilmark{2},
Stephen P. Reynolds\altaffilmark{3},
Aaron Tran\altaffilmark{1,4},
Brian J. Williams\altaffilmark{1,5}
}
%\end{CJK*}

@@

\note[Aaron]{this first draft of intro structure is mostly set (in terms of
material, number of paragraphs).}

% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
Forward shock accelerated ISM/CSM particles in young supernova remnants emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream \citep{koyama1995, reynolds1996}, producing a shell-like
morphology with bright X-ray and radio rims/filaments due to line-of-sight
projection (hereafter, thin rims).
Seminal observations \& interpretations of these filaments, interpretation in
context of DSA.
People (such as the authors of this manuscript) are trying to model these
filaments and figure out what's going on.
Why do we care about these models?  They tell us something about what happens
behind the shock, and perhaps what's going on at the shock.  We get at the
plasma turbulence, magnetic field turbulence and structure, electron injection.
Applications to: cosmic ray acceleration, turbulent field amplification, (note
assumptions in re proton/electron spectra).  Cut-off energy of injected
electrons?  Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
AGN jets, galaxy clusters \citep{van-weeren2010}, cosmological shocks?!
\citep{miniati2000, ryu2008}, other cool stuff.  See relevant reviews
\citep{blandford1987}.

% What makes these shocks?
The widths of these X-ray rims are thought to be controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  At the shock, high energy electrons efficiently radiate harder
synchrotron X-ray photons; as they are transported away from the shock, they
radiate at lower energies and lose energy more slowly.  The transport process
is driven by both bulk plasma advection away from the shock at downstream
velocity $v_d = v_s / r$, where $v_s$ is shock velocity and $r$ the compression
ratio, and diffusion ... (driven by collisionless particle interaction,
magnetic field turbulence, ????? fill in details) with respect to bulk
advection.  Energy-dependent diffusion (e.g., diffusion coefficient $D \propto
E$ for Bohm diffusion) allows higher energy electrons to diffuse further
upstream or downstream than would be expected from pure advection; in
particular, diffusion upstream of the shock may give rise to a shock precursor
\citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.  Finally, the magnetic
field strength may be quickly damped behind the shock, so that electrons may
not radiate as efficiently and thin rims would reflect the spatial structure of
the field, rather than efficient particle acceleration (and losses) and/or
efficient synchrotron cooling \citep{pohl2005}.  \note[Aaron]{I need to read up
on particle transport, diffusion, plasma physics!}

% Energy dependence.
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  Loss-limited rims should scale as $w \propto
\nu^{-1/2}$.  Diffusion weakens this energy dependence by smearing out rims at
all energies (even for energy-independent diffusion), yielding a slower
drop-off in rim widths when diffusion dominates.  Magnetic damping, at a
length scale where it may be considered a relevant control on rim widths (i.e.,
length scale comparable to filament width) predicts energy-independent rim
widths -- intuitively, if the magnetic field turns off, synchrotron radiation
turns off regardless of electron energy.  \citet{ressler2014} give a much
fuller exposition of the relative effects of advection, diffusion, and magnetic
field damping.

% Which one is right?
Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
bamba2005-hist, bamba2005-vela, parizot2006} and consequences.  Conclusion that
magnetic fields are amplified according to loss-limited model.  How could this
be plausible?  There are possible explanations -- field amplification from
plasma instabilities, evidence for stronger compression ratios?
\citep{blondin2001}.  Numerical simulations and theory on this matter
accounting for streaming instabilities, CR escape / energy losses, MHD
equations, all sorts of things I can't keep track of.  But, magnetic damping
model offers a tantalizing alternate explanation, and has not been tested.
Equivocal results by \citet{araya2010} for Cas A.
\citet{rettig2012} proposed discriminating based on filament spectra -- the
expectation is that damped spectra are softer, loss-limited harder.
\citet{ressler2014} developed the idea of investigating energy dependence and
found rim narrowing in the remnant of SN 1006, strongly favoring a loss-limited
model.

@@

% =============================
% Transport models, observables
% =============================
\section{Electron transport models}\label{sec:transport}

We briefly review relevant particle transport models that we use to fit our
measurements; a fuller review and exposition is given by \citetalias{ressler2014}.
\note[Aaron]{is it necessary to give Sean's equation numbers?  How many of the
derived equations should we give?}  In particular, the transport models
account for both advection and diffusion simultaneously, as opposed to
considering the lengthscales separately with advection dominating below a
critical energy and diffusion, above
\citep{bamba2003, vink2003, yamazaki2004, bamba2005-hist}
\note[Aaron]{clarify, be more specific}.
The effects of varying various parameters, especially in regards to filament
energy dependence, are explored in detail by \citetalias{ressler2014}.

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
%      notation is being used)
\note[Aaron]{Double check against Rettig/Pohl.  Variable definitions will be
added when equations/exposition is closer to final state.}
The electron distribution which gives rise to the observed synchrotron
radiation is injected at the forward shock and transported by advection
and plasma diffusion, following the advection-diffusion equation:
\[
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\]
By considering only steady-state transport and some other assumptions
(1-D flow (did we neglect the spherical coord terms?), neglect compressible flow?!,
space-independent diffusion coefficient):
\[
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\]
The source/sink term $C$ reflects assumptions about the injected electron
energy spectrum and its time/space evolution.
A first approximation is to treat electrons as having constant energy, but
dumping energy catastrophically after a synchrotron timescale
$\tsynch$ \note[Aaron]{define this -- either Section~\ref{sec:transport} before jumping into
transport models, or in the intro}, yielding:
\begin{equation} \label{eq:simp-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
where this is equation (5) of \citetalias{ressler2014}.
Equation~\eqref{eq:simp-mod} has a convenient analytic solution (note that
neglecting diffusion, this is $\ptl f/\ptl x \propto -f/(\tsynch v_d)$.
A more advanced model is given by accounting for continuous radiation energy
losses while electrons are transported downstream, given as:
\begin{equation} \label{eq:full-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.

Explain how the transport models constrain diffusion via $\mE$, define $\mE$.
Explain how we back out a filament shape/width from these models

\subsection{Energy dependent widths, diffusion}

Bohm diffusion: $D(E) = \eta C_d E / B$. Generalized diffusion writen as:
\[
    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
\]
Explain the use of fiducial energy -- this makes sense and eases discussion,
but linking $E_h$ and $\eta_2$ to $\eta$ and plain Bohm diffusion seems a bit
murky.

For the simple model, we have equation (6) of \citetalias{ressler2014}:
\begin{equation} \label{eq:simp-width}
    a = \frac{2 D / v_d}{ \sqrt{ 1 + \frac{4D}{v_d^2 \tau_{\mt{synch}}}} - 1}
\end{equation}
which we relate to full width half max by projection factor $\beta = 4.6$
so that $w = \beta a$, assuming (1) electron distribution exponential in radial
coordinate $x$, and (2) spherical source \note[Aaron]{shell?}
\citep{ballet2006}.

For the full model (equation~\eqref{eq:full-mod}), we numerically solve for
electron distribution $f(E,x)$ using solutions due to \citet{lerche1980} and
\citet{rettig2012}; DETAILS.
Ultimately, we integrate numerically computed electron distributions $f(E,x)$
over energy to obtain synchrotron emissivity as
\[
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\]
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is the one-particle synchrotron
emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight yields
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.

\subsection{Tycho parameters}

Give numbers ($v_s$, $v_d$, $r_s$, etc.).  Give a definition of the cut-off
energy following Rettig and Pohl (again cite Sean's paper).
We use an electron spectrum cut-off energy of:
\begin{align*}
    E_{\mt{cut}} =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \\
        &\times \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
        \left[
            \frac{E_h^{\mu - 1}}{\eta}
        \right]^{1 / (1 + \mu)}
\end{align*}
which is equation~(19) of \citetalias{ressler2014}.
\note[Aaron]{This differs from Sean's presentation -- I drew this from the
Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
$E_h$ ?!  Come back to this shortly.}

Discuss $\mE$, I have NOT defined this quantity below.  % TODO

@@

We also consider a magnetically damped field of form
\[
    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
\]
following \citetalias[Section 3.2]{ressler2014}.

@@

All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function.
Looking at proposer's guide, Figure 4.13 -- the off-axis PSF should
still have FWHM of $\abt 1\arcsec$ at $4\arcmin$ (approx. Tycho's radius).
Is that good enough for us?

@@

% Fit data to models
We fit the two transport models given by Equations~\eqref{eq:simp-mod} and
\eqref{eq:full-mod} to our measured rim widths as a function of energy.
Although our measured radial profiles sum a continuous energy range of counts,
we assigned each width measurement to the lower energy limit of its band
(e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
model profile widths at $0.7 \unit{keV}$) \note[Aaron]{bad wording}.
We also averaged the positive and negative error bars on each FWHM measurement
(Table~\ref{tab:fwhms}) for least squares fitting.
% Averaging/merging/synthesizing, somehow, our results
Rim widths from each region are fitted separately; we consider filament and
remnant-wide physical parameters by averaging best fit parameters for each
region in Section~\ref{sec:fit-results}.

% Model knobs and how we twiddled them
We have three parameters to vary (more if we consider magnetic damping).
They are diffusion-energy scaling exponent $\mu$, normalized diffusion
coefficient $\eta_2$, and magnetic field strength $B_0$.
Explain why we are fixing $\mu$ (forward reference best fit figures).
We consider $\mu = 0$, 1/3, 1/2, 1, 1.5, and 2; recall that $\mu = 1/3$ and $1/2$
respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
energy spectra.  As $\eta_2$ is highly variable in our fits, we also consider
fits with $\eta_2 = 1$ fixed, coincident with Bohm diffusion at $2 \unit{keV}$.

A few remnant-specific parameters enter into the model calculations.  We take
electron spectral index $s = 2.3$ (from radio spectral index $\alpha = 0.65$,
\citet{kothes2006} \note[Aaron]{not using $0.58$ from Green's catalog?!}),
remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
a factor of 2; we interpolated shock velocities reported by
\citet{williams2013} to estimate individual shock velocities for each region.
\note[Aaron]{this paragraph might belong in Section~\ref{sec:transport}?}

% How to do the fit
The simple model is readily fit from equation~\eqref{eq:simp-width}.
The full model is numerically computed following the procedure laid out in
\emph{section ?!}, yielding intensity profiles from equation~\eqref{eq:intensity} for each
energy band and hence a model full width at half maximum.
For least squares fitting purposes, the full model is treated as a black box
that takes in physical parameters
% TODO modify tables to match what is stated here -- in regards to parameters
% being effectively unbounded.
% TODO for extreme values in tables -- go back and double check chi^2 space
To perform full model fits, we tabulated a large grid for fixed values of $\mu$
and shock velocity $v_s$.  If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10
\unit{mG}$, we deem it effectively unconstrained (only a few fits do so, and
only to the $\eta_2$ limit).  Note that we do not allow / consider fits with
$\eta_2$ negative (may be trivial, just note parameter bounds).  As the full
continuous loss model must be numerically solved, its predicted rim widths are
subject to resolution error in the numerical integrals.  We chose our
integration resolutions such that the fractional error associated with
halving/doubling our resolution is less than $1\%$ for the parameter space
relevant to our filaments.
\note[Aaron]{rewrite -- unclear.  Need to verify
1\% claim and check Pacholczyk table resolution (and possibly Bessel
function numbers)...}

@@

@@

Diffusion coefficient $\eta_2$, on the other hand, is a bit of a mess.

>>>>

%\begin{CJK*}{UTF8}{gbsn}
\author{
Aaron Tran\altaffilmark{1,4},
Brian J. Williams\altaffilmark{1,5},
Robert Petre\altaffilmark{1},
Sean M. Ressler\altaffilmark{2},
Stephen P. Reynolds\altaffilmark{3}
}
%\end{CJK*}

@@

\note[Aaron]{this first draft of intro structure is mostly set (in terms of
material, number of paragraphs).  Explanations/etc may be too simplistic, I
have more reading to do.}

% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
Forward shock accelerated ISM/CSM particles in young supernova remnants emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream \citep{koyama1995, reynolds1996}, producing a shell-like
morphology with bright X-ray and radio rims/filaments due to line-of-sight
projection (hereafter, thin rims).
Seminal observations \& interpretations of these filaments, interpretation in
context of DSA.  Attempts to model filaments and figure out what's going on.
Why do we care about these models?  They tell us something about what happens
behind the shock, and perhaps what's going on at the shock.  We get at the
plasma turbulence, magnetic field turbulence and structure, electron injection.
Applications to: cosmic ray acceleration, turbulent field amplification, (note
assumptions in re proton/electron spectra).
Cut-off energy of injected
electrons?  Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
AGN jets, galaxy clusters \citep{van-weeren2010}, and even cosmological shocks
\citep{miniati2000, ryu2008}.  See relevant reviews \citep{blandford1987}.

% What makes these shocks?
The widths of these X-ray rims are thought to be controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and diffusion (\emph{driven by
collisionless particle interaction, magnetic field turbulence, ?????  fill in
details}) with respect to bulk advection.  Energy-dependent diffusion (e.g.,
diffusion coefficient $D \propto E$ for Bohm diffusion) allows higher energy
electrons to diffuse further upstream or downstream than would be expected from
pure advection; in particular, diffusion upstream of the shock may give rise to
a shock precursor \citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.
Finally, the magnetic field strength may be quickly damped behind the shock, so
that electrons may not radiate as efficiently and thin rims would reflect the
spatial structure of the field, rather than efficient particle acceleration
(and losses) and/or efficient synchrotron cooling \citep{pohl2005}.

% Energy dependence.
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  Synchrotron loss-limited rims should scale as $w
\propto \nu^{-1/2}$.  Diffusion smears out rims at all energies with stronger
effect at higher energies, yielding a slower drop-off in rim widths when
diffusion dominates.  Magnetic damping, if at a length scale comparable to
filament widths, predicts energy-independent rim widths -- intuitively, if the
magnetic field turns off, synchrotron radiation turns off regardless of
electron energy.  \citet{ressler2014} give a much fuller exposition of the
relative effects of advection, diffusion, and magnetic field damping.

% Which one is right?
Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
bamba2005-hist, bamba2005-vela, parizot2006} and consequences.  Conclusion that
magnetic fields are amplified according to loss-limited model.  How?  Field
amplification from plasma instabilities, evidence for stronger compression ratios?
\citep{blondin2001}.  Lots of numerical and theoretical work that I don't
understand.

Introduce $\tsynch$ and the basic intuition.
Explain why diffusion is an important consideration
(when did this start being recognized as relevant?).

Previous work that accounted for advection/diffusion alone or separately,
previous work that considered both simultaneously (as we do here).

But, magnetic damping offers a tantalizing alternate explanation and has not
been fully tested.  Equivocal results by \citet{araya2010} for Cas A.
\citet{rettig2012} proposed discriminating based on filament spectra -- the
expectation is that damped spectra are softer, loss-limited harder.
\citet{ressler2014} developed the idea of investigating energy dependence and
found rim narrowing in the remnant of SN 1006, strongly favoring a loss-limited
model.

@@

% TODO Chunk of text I don't know what to do with...
We briefly review relevant particle transport models that we use to fit our
measurements; a fuller review and exposition is given by \citetalias{ressler2014}.
In particular, the transport models
account for both advection and diffusion simultaneously, as opposed to
considering the lengthscales separately with advection dominating below a
critical energy and diffusion, above
\citep{bamba2003, vink2003, yamazaki2004, bamba2005-hist}
\note[Aaron]{clarify, be more specific}.
The effects of varying various parameters, especially in regards to filament
energy dependence, are explored in detail by \citetalias{ressler2014}.

% =============================
% Transport models, observables
% =============================
\section{Nonthermal rim modeling}\label{sec:models}

\subsection{Particle transport}\label{sec:transport}

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
%      notation is being used)
% TODO double check equations, exposition against Rettig/Pohl and others
% TODO review variable definitions when closer to final draft
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
transport from initial injection at the remnant's forward shock as following
the advection-diffusion equation given by:
\note[Aaron]{ApJ prefers bold vectors and vector operators, fix later}
% TODO fix vector operators
\begin{equation}
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\end{equation}
where $f = f(E,x)$ is electron distribution as a function of electron energy
$E$ and downstream distance $x$ (where the forward shock is at $x=0$ and
$x>0$ towards the remnant's interior); $C$ is an arbitrary source/sink term,
$D$ is the diffusion coefficient, and $\vec{v}$ is a velocity field.
By considering 1-D steady-state plane transport at a constant downstream
velocity $v_d$ \note[Aaron]{we threw out 1. spherical coordinate terms, and 2.
compressible flow terms, I think.  Is the latter justifiable?  Makes sense for
assumption of uniform downstream velocity -- but is this a safe assumption in
practice?  Double check order-of-magnitude...} and a space-independent diffusion
coefficient, we obtain:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
The source/sink term $C$ is determined by our assumptions about the injected
electron energy spectrum and its time/space evolution.

A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary as $B=B(x)$.  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
which is equation (5) of \citetalias{ressler2014}.
\note[Aaron]{I think there should be a delta function for e- injection, but it
probably doesn't affect the solution.  Double check.}
Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
\exp(-x/a)$ where $a$ is a characteristic scale length.  The full width half
maximum (FWHM) of a thin rim produced by this ``simple'' model is given by:
\begin{equation} \label{eq;simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
where $\beta$ is a projection factor relating $w$ to $a$ as $w = \beta a$.  We
take $\beta = 4.6$ assuming projection from spherical shell, as derived by
\citet{ballet2006}.

A more advanced model is given by accounting for continuous radiation energy
losses while electrons are transported downstream:
\begin{equation} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.  The injected electron
distribution is an exponentially cut-off power law with normalization $K_0$ and
cut-off energy $E_{\mt{cut}}$; the expression for the cut-off energy is
determined by the form of the diffusion coefficient $D$, which we discuss in
Section~\ref{sec:diffcoeff}.  To determine rim profiles and widths, we
numerically solve for electron distribution $f(E,x)$ using Green's function
solutions due to \citet{lerche1980} and \citet{rettig2012}; the equations are
given using notation close to that of this paper by \citetalias{ressler2014}.
The electron distribution may then be integrated to obtain synchrotron
emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron
emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical shell yields intensity:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  We can then compute these
integrals (equations~\eqref{eq:emissivity},~\eqref{eq:intensity}) to obtain
model predictions for rim FWHMs.

\subsection{Diffusion energy-dependence} \label{sec:diffcoeff}

Explain how the transport models constrain diffusion via $\mE$, define $\mE$.
Explain the basic interplay between diffusion and magnetic field, in
controlling rim widths.

Bohm diffusion: $D(E) = \eta C_d E / B$. Generalized diffusion writen as:
\begin{equation}
    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
\end{equation}
Explain the use of fiducial energy -- this makes sense and eases discussion,
but linking $E_h$ and $\eta_2$ to $\eta$ and plain Bohm diffusion seems a bit
murky.

Mention that different $\mu$ values arise from particular models of turbulence.

We use an electron spectrum cut-off energy of:
\begin{align*}
    E_{\mt{cut}} =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \\
        &\times \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
        \left[
            \frac{E_h^{\mu - 1}}{\eta}
        \right]^{1 / (1 + \mu)}
\end{align*}
which is equation~(19) of \citetalias{ressler2014}.
\note[Aaron]{This differs from Sean's presentation -- I drew this from the
Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
$E_h$ ?!  Come back to this shortly.}

@@

We also consider (not really) a magnetically damped field of form
\begin{equation}
    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
\end{equation}
following \citetalias[Section 3.2]{ressler2014} and \citet{pohl2005}.

@@

All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function.
Looking at proposer's guide, Figure 4.13 -- the off-axis PSF should
still have FWHM of $\abt 1\arcsec$ at $4\arcmin$ (approx. Tycho's radius).
Is that good enough for us?
(Cassam-Chena\"i et al. considered PSF effects when modeling rim widths, though
it doesn't look like it made a big difference?)

@@

% Fit data to models
We fit the two transport models given by Equations~\eqref{eq:simp-mod} and
\eqref{eq:full-mod} to our measured rim widths as a function of energy.
We assigned each width measurement to the lower energy limit of its energy band
(e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
model profile widths at $0.7 \unit{keV}$) \note[Aaron]{bad wording}.
We also averaged the positive and negative error bars on each FWHM measurement
(Table~\ref{tab:fwhms}) for least squares fitting.
% Averaging/merging/synthesizing, somehow, our results
Rim widths from each region are fitted separately; we consider filament and
remnant-wide physical parameters by averaging best fit parameters for each
region in Section~\ref{sec:fit-results}.

% Model knobs and how we twiddled them
We have three parameters to vary (more if we consider magnetic damping):
diffusion-energy scaling exponent $\mu$, normalized diffusion
coefficient $\eta_2$, and magnetic field strength $B_0$.
To make our nonlinear fitting tractable, we fix $\mu$ in all fits and
consider $\mu = 0$, 1/3, 1/2, 1, 1.5, and 2; recall that $\mu = 1/3$ and $1/2$
respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
energy spectra.  As $\eta_2$ is highly variable in our fits, we also consider
fits with $\eta_2 = 1$ fixed, coincident with Bohm diffusion at $2 \unit{keV}$.

A few remnant-specific parameters enter into the model calculations.  We take
electron spectral index $s = 2.3$ (from radio spectral index $\alpha = 0.65$,
\citet{kothes2006} \note[Aaron]{not using $0.58$ from Green's catalog?!}),
remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
a factor of 2; we interpolated shock velocities reported by
\citet{williams2013} (rescaled to $3 \unit{kpc}$ rather than $2.3 \unit{kpc}$
to estimate individual shock velocities for each region.
\note[Aaron]{this paragraph might belong in an earlier section?}

% How to do the fit
Our data are readily fit to the simple model by equation~\eqref{eq:simp-width}.
The full model is numerically computed as detailed in
Section~\ref{sec:transport}, yielding intensity profiles and hence model FWHMs
in each energy band.
For least squares fitting purposes, the full model is treated as a black box
that takes in physical parameters
% TODO modify tables to match what is stated here -- in regards to parameters
% being effectively unbounded.
% TODO for extreme values in tables -- go back and double check chi^2 space
To perform full model fits, we tabulated a large grid for fixed values of $\mu$
and shock velocity $v_s$.  If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10
\unit{mG}$, we deem it effectively unconstrained (only a few fits do so, and
only to the $\eta_2$ limit).  Note that we do not allow / consider fits with
$\eta_2$ negative (may be trivial, just note parameter bounds).  As the full
continuous loss model must be numerically solved, its predicted rim widths are
subject to resolution error in the numerical integrals.  We chose our
integration resolutions such that the fractional error associated with
halving/doubling our resolution is less than $1\%$ for the parameter space
relevant to our filaments.
\note[Aaron]{rewrite -- unclear.  Need to verify
1\% claim and check Pacholczyk table resolution (and possibly Bessel
function numbers)...}

@@

X-ray rims are not damped -- could damping be relevant to the radio rims?

@@

Diffusion coefficient $\eta_2$, on the other hand, is a bit of a mess.
Would it be useful to report advective and diffusive lengthscales at 2 keV?
Idea being that it is hard to intuit what the large numbers even mean.
(especially for the simple model -- it sits on a plateau in chi-squared space
where small $\eta_2$ may be disfavored, but beyond a certain point any $\eta_2$
will do)
